Guarded Recursion in Agda via Sized Types

### 2019-02-08 code-oneclock-paper/latex/paper.tex
6)

Finally, we would like to understand whether sized types can be simulated using guarded recursion.
Sized types require dependent types and subtyping, which \GTT\ does not have.
We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.
%%
%% Bibliography
%%

>>>>

Finally, we would like to understand whether sized types can be
simulated using guarded recursion.
This could either be done by modeling sized types in a topos of
trees-like category \cite{BMSS-synthetic,MannaaM18} or via the
encoding of a type theory with sized types into a dependent type
theory for guarded recursion such as Clocked Type Theory
\cite{BahrGM17}. 
%Sized types require dependent types and subtyping, which \GTT\ does not have.
%We conjecture that Clocked Type Theory \cite{BahrGM17} can model sized types with explicit subtyping.

%%
%% Bibliography
%%
